The purpose of this project was to create a distributed chat application working on at least two separate platforms with a running server. For this purpose we, a team of 4, chose to implement a solution for web clients and android clients as well as a server running as a Java application. This was an opportunity for us to experience working together as a software development team, as well as to learn to communicate effectively, distribute tasks, and manage our time for a large piece of work.

\section{Problem being addressed}

Currently many chat solutions exist, each of which may focus on a particular priority - whether it is user experience, security, speed, or convenience in use with other applications. These are discussed in more depth in section \ref{lit-review}. Our project, Team Zero Chat Application, addresses several problems: 

\begin{itemize}
  \item Secrecy - all users text messages are encrypted securely using encryption protocols (see section \ref{encryption}). The server can see encrypted messages but has no access to keys or knowledge of the encryption.
  \item Accessibility - Anyone with an Android client or access to a web browser can register and start using the application.
  \item Anonymity and Privacy - No affiliation with third party market research companies (chat metadata stored but not shared), and no requirement to associate with a phone number.
  \item Simple - Just text messaging, between pairs or groups, and no extra clutter.
\end{itemize}

\section{Summary of achievements}
\label{summary_achievements}

We implemented a chat application that allows users to register, login, and chat with anyone who is also registered. User details are stored in the database, and passwords are stored securely. All chat messages are encrypted using a combination of public key encryption and symmetric AES encryption (see section \ref{encryption} for details). Chat history is stored in encrypted form and can be retrieved on request. Group chat functionality is also supported. Users can search for other users and can see if they are online. Chat messages sent when a user is offline will be sent automatically on login. These functionalities will be covered in detail in this report.

Of the requirements determined in the initial phase of the project (see section \ref{requirements}, we were able to implement 94 \% of all priority 1-3 requirements.
